<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Demo: how to extract genomic profiles wiht metagene}
-->

Demo: how to extract genomic profiles wiht metagene
========================================================

### 0. Introduction

In this demo, we will see how it is possible to use metagene to extract the
genomic profiles from bam files.

### 1. Preparing the files

We will work with the following bam files:

```{r getBamFilenames}
bam_files <- c("inst/extdata/H3K4me1.bam", "inst/extdata/H3K27ac.bam")
#bam_files <- c(system.file("extdata/H3K4me1.bam", package = "ProfilesMetagene"),
#               system.file("extdata/H3K27ac.bam", package = "ProfilesMetagene"))
```

We will use the following regions:

```{r getRegions, cache = TRUE}
regions <- "inst/extdata/tidy_enhancers.txt"
regions <- read.table(regions, header = TRUE)
regions <- makeGRangesFromDataFrame(regions, start.field = "chromStart",
               end.field = "chromEnd")
width(regions) <- 1000
```

We also need to make sure the `seqlevels` of the regions match the `seqlevels`
of the bam files:

```{r matchSeqlevels}
seqlevels(regions, force = TRUE) <- seqlevels(Rsamtools::BamFile(bam_files[1]))
```

### 2. Launching the metagene analysis

```{r metagene, cache = TRUE}
suppressMessages(library(metagene))
mg <- metagene$new(regions = regions, bam_files = bam_files, cores = 12)
```

### 3. Extracting the profiles

```{r extractProfiles}
profiles <- mg$coverages
```
